\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2015-04-07 paper/paper.tex
Fixed GHz thing in paper :D

\subsection{Experiment Setup}
For the testing, a single laptop was used to collect all the timed data. The tests were run in JetBrains' PyCharm, using the built-in functions to run the python code. The python interpreter used was Python 3.4 and the laptop was running Windows 10 Pro Technical Preview (at 3.5 GHz and 8.00 GB) at the time of the testing. Efforts were made to ensure all the testing was performed under the same circumstances.

>>>>

\subsection{Experiment Setup}
For the testing, a single laptop was used to collect all the timed data. The tests were run in JetBrains' PyCharm, using the built-in functions to run the python code. The python interpreter used was Python 3.4 and the laptop was running Windows 10 Pro Technical Preview (at 3.75 GHz (average speed, max 3.9 GHz) and 8.00 GB) at the time of the testing. Efforts were made to ensure all the testing was performed under the same circumstances.
